---
title: 'Lab template'
subtitle: "STATS 369"
author: "Your name"
output:
  html_document:
    highlight: pygments
    theme: readable
    toc: true
    toc_depth: 2
    toc_float: true
---

*It is good practice to have all your general set up at the start of your document. Imagine this is the beginning of a new Rmd. This is where I would set any general chunk options, as well as where I would load my libraries. If I realise I need additional libraries later, I would come back here and add them.*

*Notes from me are in italics.*

```{r setup, message = FALSE}
# Set code to show
knitr::opts_chunk$set(echo = TRUE)

# Load libraries
library(tidyverse)

library(glue) # awesome package that we don't have time to talk about
library(lubridate) # helps make dates much easier

library(TMDb) # provides access to the API
library(keyring) # for storing our API key

library(polite)
```







## Task 1

*Use headings to organise your submission and make it easy for your marker to find your answers*

```{r}
# Is the hashtag/octothrope is inside a code chunk, then it is a comment
# You will be expected to comment your code sufficiently clearly
# so that others with reasonable R knowledge could follow your work
```


## Task 2

An example of some commentary about my work...

```{r}
# Some commented code
x = 2+2
```

The result of my calculation is `r x`. That is some inline R code being run!

I can also multiply by 10 to get `r x*10`.




















