---
title: 'Lab template'
subtitle: "STATS 369"
author: "Your name"
output:
  html_document:
    highlight: pygments
    theme: readable
    toc: true
    toc_depth: 2
    toc_float: true
---

*It is good practice to have all your general set up at the start of your document. Imagine this is the beginning of a new Rmd. This is where I would set any general chunk options, as well as where I would load my libraries. If I realise I need additional libraries later, I would come back here and add them.*

*Notes from me are in italics.*

```{r setup, message = FALSE}
# Set code to show
knitr::opts_chunk$set(echo = TRUE)

# Load libraries
library(tidyverse)

library(glue) # awesome package that we don't have time to talk about
library(lubridate) # helps make dates much easier

library(TMDb) # provides access to the API
library(keyring) # for storing our API key

library(polite)
```

## Task 1

*Use headings to organise your submission and make it easy for your marker to find your answers*

```{r}
# Bow
bow_imdb <- bow("https://www.imdb.com/search/keyword/?keywords=christmas&ref_=kw_nxt&sort=moviemeter,asc&mode=detail&page=2&title_type=movie")
bow_imdb
```
The default crawl delay for the IMDB website is 5 seconds
_________________________________________________________

## Task 2

No, we can't ethically scrape IMDB without their permission. Despite the polite message saying the path is able to be scraped, we should not scrape IMDB because in their T's and C's they explicitly say that "You may not use data mining, robots, screen scraping, or similar data gathering and extraction tools on this site, except with our express written consent as noted below." (from https://www.imdb.com/conditions). As we do not have explicit written permission, it is unethical to scrape IMDB.

```{r}
# Sign in
# key_set("TMDB_API")
# b58beee5ecf98a1792d3d9fb24a5c1b1
```


## Task 3

```{r}
genres = read_csv("genres.csv")
head(genres)
```
This dataset is not tidy.

Making it tidy:

```{r}
tidy_genres = pivot_longer(genres, cols = "28":"37", names_to = "number", values_to = "genre")
head(tidy_genres)
```

```{r}
# From Liza
search_keyword <- function(api_key, query, page=1){
    if(page<1 || page>1000){
        stop("page must be a number between 1 and 1000")
    }
    l <- list(page=page)
    l <- l[!is.na(l)]
    
    params <- paste("&", names(l), "=",l, sep="", collapse="")
    url <- fromJSON(GET(URLencode(url<-
                                    paste(                          "http://api.themoviedb.org/3/search/keyword?api_key=",
                                      api_key,
                                      "&query=",
                                      query,
                                      params,
                                      sep = ""
                                    )))$url)
    
    return(url)
}
```

```{r}
# a function that runs this for command for any given page
one_page <- function(x) search_keyword(key_get("TMDB_API"), query = "christmas", page = x)

# a vector of the pages, from 1 to the max page for this search
pages <- 1:one_page(1)$total_pages

# now use map_dfr (map specifcally for returning data frames) instead of a for loop
christmas_keywords <- map_dfr(pages, function(x) one_page(x)$results)
christmas_keywords
```


## Task 4: Find a set of key word you're interested in

```{r}
alien_page <- function(x) search_keyword(key_get("TMDB_API"), query = "alien", page = x)
alien_pages <- 1:alien_page(1)$total_pages
alien_keywords <- map_dfr(alien_pages, function(x) alien_page(x)$results)
head(alien_keywords)
```

Searching for movies and writing to a new csv file:

## Task 5 - Set up a search of your own

```{r}
# search for all alien sci-fi movies
alien_ids <- glue_collapse(alien_keywords$id, sep="|")

alien_sci_fi <- function(x) discover_movie(key_get("TMDB_API"), 
                                       with_genres = 878, 
                                       with_keywords = alien_ids, 
                                       page = x)
alien_sf_pages <- 1:alien_sci_fi(1)$total_pages
aliens_sf <- map_dfr(alien_sf_pages, function(x) alien_sci_fi(x)$results)
head(aliens_sf)
write_csv(aliens_sf, "aliens_sci_fi.csv")

```


## Task 6 - Ugly Graph

```{r}

ggplot(aliens_sf, aes(vote_average, log(sqrt(vote_count)+4)-pi, col=id)) + geom_line() + theme(plot.background = element_rect(fill="blue"))

```



THIS IS VERY UGLY INDEED



