---
title: "Lab2"
output: html_document
date: "2023-07-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Imports
library(tidyverse)
```

```{r}
# Download Data
path <- "http://archive.ics.uci.edu/ml/machine-learning-databases/abalone/"
abalone <- read.csv(paste(path,"abalone.data",sep=""), header = FALSE)
names(abalone) <- c("Type", "Length", "Diameter", "Height", "Whole.weight",
"Shucked.weight", "Viscera.weight", "Shell.weight", "Rings")
summary(abalone)
```

```{r}
#Drop 10% of the data
nMissing <- 400
nData <- dim(abalone)[1]
thisData <- abalone
set.seed(1)
missingInd <- sample(1:nData,size=nMissing,replace=FALSE)
thisData$Rings[missingInd] <- NA
```

Estimation using complete data
Start by computing a 95% confidence interval for the mean age of the paua in the population using only
complete data (be careful to account for the relationship between age and number of rings). note that the output from the earlier summary function tells us the sample average is about **11.434**

```{r}
TrueMean=11.434


MeanIgnoreNA = t.test(thisData$Rings+1.5, na.rm=TRUE)
```

The `MeanIgnoreNA` is `r MeanIgnoreNA$conf.int`, which is slightly off the true value.
the error is `r MeanIgnoreNA$conf.int - TrueMean`


Estimation using mean imputation

```{r}
SampleMean = mean(thisData$Rings,na.rm=TRUE)
MeanImputeNA = thisData$Rings %>% as.numeric() %>% replace_na(SampleMean) %>% +1.5 %>% t.test()

```

The `MeanImputeNA` is `r MeanImputeNA$conf.int`, which is slightly off the true value.
the error is `r MeanImputeNA$conf.int - TrueMean`

Estimate using hot deck implementation

```{r}
set.seed(2)
thisData$Type <- as.factor(thisData$Type)
impData <- thisData$Rings
for (t in levels(thisData$Type)) {
  thisMissing <- thisData %>% filter(Type==t) %>% is.na() %>% as.data.frame()
  numDraws <- thisMissing$Rings %>% sum()
  hotDeck <- !ThisMissing$Rings %>% sample(numDraws, replace = TRUE) #With replacement
  #impData[thisMissing]<-hotDeck
}



```





























