---
title: "Lab2"
output: html_document
date: "2023-07-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Imports
library(tidyverse)
```

```{r}
# Download Data
path <- "http://archive.ics.uci.edu/ml/machine-learning-databases/abalone/"
abalone <- read.csv(paste(path,"abalone.data",sep=""), header = FALSE)
names(abalone) <- c("Type", "Length", "Diameter", "Height", "Whole.weight",
"Shucked.weight", "Viscera.weight", "Shell.weight", "Rings")
summary(abalone)
```

```{r}
#Drop 10% of the data
nMissing <- 400
nData <- dim(abalone)[1]
thisData <- abalone
set.seed(1)
missingInd <- sample(1:nData,size=nMissing,replace=FALSE)
thisData$Rings[missingInd] <- NA
```

Estimation using complete data
Start by computing a 95% confidence interval for the mean age of the paua in the population using only
complete data (be careful to account for the relationship between age and number of rings). note that the output from the earlier summary function tells us the sample average is about **11.434**

```{r}
TrueMean=11.434


MeanIgnoreNA = t.test(thisData$Rings+1.5, na.rm=TRUE)
```

The `MeanIgnoreNA` is `r MeanIgnoreNA$conf.int`, which is slightly off the true value.
the error is `r MeanIgnoreNA$conf.int - TrueMean`


Estimation using mean imputation

```{r}
SampleMean = mean(thisData$Rings,na.rm=TRUE)
MeanImputeNA = thisData$Rings %>% as.numeric() %>% replace_na(SampleMean) %>% +1.5 %>% t.test()

```

The `MeanImputeNA` is `r MeanImputeNA$conf.int`, which is slightly off the true value.
the error is `r MeanImputeNA$conf.int - TrueMean`

Estimate using hot deck implementation

```{r}
set.seed(2)
thisData$Type <- as.factor(thisData$Type)
impData <- thisData$Rings
for (t in levels(thisData$Type)) {
  thisMissing <- thisData$Type==t & is.na(thisData$Rings)
  numDraws <- thisMissing %>% sum()
  hotDeck <- thisData$Rings[thisData$Type==t & !is.na(thisData$Rings)] %>% sample(numDraws, replace = TRUE) #With replacement
  impData[thisMissing]<-hotDeck
}

MeanHotDeck = impData %>% as.numeric() %>% +1.5 %>% t.test() 


```

The `MeanHotDeck` is `r MeanHotDeck$conf.int`, which is slightly off the true value.
the error is `r MeanHotDeck$conf.int - TrueMean`


BOOTSTRAP:

```{r}
# Bootstrapping
set.seed(3)
numBoots <- 200
bootReps <- numeric(numBoots)
for (i in 1:numBoots) {
  thisBootInd <- sample(4177, replace = TRUE)
  thisBoot <- thisData[thisBootInd,]

  for (t in levels(thisData$Type)) {
    thisMissing <- thisBoot$Type==t & is.na(thisBoot$Rings)
    numDraws <- thisMissing %>% sum()
    hotDeck <- thisBoot$Rings[thisBoot$Type==t & !is.na(thisBoot$Rings)] %>% sample(numDraws, replace = TRUE) #With replacement
    thisBoot$Rings[thisMissing]<-hotDeck
  }
  bootReps[i] <- mean(thisBoot$Rings+1.5)
}

actualEstimate <- mean(impData+1.5)
Iemp2 <- c(2*actualEstimate,2*actualEstimate)-quantile(bootReps,c(0.975,0.025))
Iemp2

```

The Mean from our BootStrapping is `r Iemp2`.

```{r}
theta_boot <- (1/numBoots)*sum(bootReps)
V_boot <- (1/(numBoots-1))*sum((bootReps-theta_boot)^2)
Inorm <- c(theta_boot-qnorm(0.975)*sqrt(V_boot),theta_boot+
qnorm(0.975)*sqrt(V_boot))
Inorm
```

Alternatively, The Mean from our BootStrapping is `r Inorm`.



Task: Estimation using multiple imputation

```{r}
set.seed(4)
nImps <- 500
MIEst <- numeric(nImps)
MIvar <- numeric(nImps)
for (i in 1:nImps) {
  impData <- thisData$Rings
  for (t in levels(thisData$Type)) {
    thisMissing <- thisData$Type==t & is.na(thisData$Rings)
    numDraws <- thisMissing %>% sum()
    hotDeck <- thisData$Rings[thisData$Type==t & !is.na(thisData$Rings)] %>% sample(numDraws, replace = TRUE)
    impData[thisMissing]<-hotDeck
  }
  # Calculate mean and variance
  MIEst[i] <- impData %>% as.numeric() %>% mean()
  MIvar[i] <- 1/4177 * 1/4176 * sum((impData-MIEst[i])**2)
}
# Point Estimate
ptEst <- mean(MIEst+1.5)
ptEst

```

```{r}
#Within Imp Variance
WEst <- 1/nImps * sum(MIvar)
WEst
```

```{r}
# Between
BEst <- 1/(nImps-1) * sum((ptEst-(MIEst+1.5))**2)
BEst
```


```{r}
# Estimate of fraction of info lost due to missing data
TEst <- WEst+((nImps+1)/nImps)*BEst
gamma <- (nImps+1)/nImps * BEst / TEst
gamma

```

```{r}
#Degrees of freedom and conf interval
df <- (nImps-1)*(1 + 1/(nImps+1)*WEst/BEst)**2
wdth <- ***K***
c(ptEst-wdth,ptEst+wdth)

```
















