---
title: 'Lab template'
subtitle: "STATS 369"
author: "Your name"
output:
  html_document:
    highlight: pygments
    theme: readable
    toc: true
    toc_depth: 2
    toc_float: true
---

*It is good practice to have all your general set up at the start of your document. Imagine this is the beginning of a new Rmd. This is where I would set any general chunk options, as well as where I would load my libraries. If I realise I need additional libraries later, I would come back here and add them.*

*Notes from me are in italics.*

```{r setup, message = FALSE}
# Set code to show
knitr::opts_chunk$set(echo = TRUE)

# Load libraries
library(tidyverse)
library(ISLR2)

```

## Task 1

*Use headings to organise your submission and make it easy for your marker to find your answers*

```{r}
# Read in advertising data set
adverts = read_csv("Advertising.csv", show_col_types = F)

# Fit a model
model = lm(sales~TV+radio+newspaper, data=adverts)
tib = as_tibble(summary(model)$coeff) %>% rename("t-statistic"="t value", "p-value"="Pr(>|t|)", "Coefficient"="Estimate")

tib$"t-statistic" = round(tib$"t-statistic", 2)
tib$"Std. Error" = round(tib$"Std. Error", 4)
tib$"Coefficient" = round(tib$"Coefficient", 3)

tib$"p-value" = ifelse(tib$"p-value"<0.0001, "<0.0001", round(tib$"p-value", 4))

ads = as.data.frame(tib)
rownames(ads) <- c("Intercept","TV","radio","newspaper")

knitr::kable(ads, align="c")
```
**Describe the null hypotheses:**

The null hypothesis for the intercept, is that the y-intercept=0. Interpreted in the context of the problem, this would mean that for 0 advertising in every area, would result in 0 sales. Clearly based on the p-value there is strong evidence against this null hypothesis.

The null hypothesis for the other three rows, i.e. for the TV, newspaper and radio, is that the coefficient for that explanatory variable is 0, i.e. that they have NO effect on the sales. The P-value for the TV and radio advertising is very small, providing much evidence against this assumption. For newspaper advertising however, the P-value is large, meaning that there is very little evidence against this null hypothesis.

To conclude, based on our P-values, we can see that the newspaper advertising is uneffective, but the TV and radio advertising is effective.

## Task 2




































